Plots and tables summarizing results of Poisson simulations

### 2019-11-12 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

Here we create plots and tables to compare various methods, including
SMASH, for reconstructing a spatially structured signal from
Poisson-distributed data. Similar to the Gaussian simulations, we
generated data sets using a variety of test functions and intensity
ranges. Specifically, we considered 6 test functions, rescaling the
test function so that the smallest intensity was x and the largest
intensity was y, with (x,y) set to either (1/100, 3), (1/8, 8) or
(1/128, 128). For each combination of test function and intensity
range, we simulated 100 data sets. In the plots and tables below, we
summarize the error (MISE) in the estimates computed in the 100 data
sets from each simulation setting.

@@

Load the ggplot2 cowplot and xtable packages.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
library(xtable)
```

@@

```{r spikes-table, results="asis"}
mise.s.table <- cbind(mise.s.1[methods],
                      mise.s.8[methods],
                      mise.s.128[methods])
rownames(mise.s.table) <- table.row.names
colnames(mise.s.table) <- table.col.names
print(xtable(mise.s.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

@@

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
                                     mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
create.violin.plots <- function (pdat1, pdat8, pdat128) {
  p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
		theme_cowplot() +
		theme(axis.line = element_blank())
  p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
		theme_cowplot() +
		theme(axis.line = element_blank())
  p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
		theme_cowplot() +
		theme(axis.line = element_blank())
  return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))
}
create.violin.plots(pdat1,pdat8,pdat128)
```

>>>>

Here we create plots and tables to compare various methods, including
SMASH, for reconstructing a spatially structured signal from
Poisson-distributed data. Similar to the Gaussian simulations, we
generated data sets using a variety of test functions and intensity
ranges. Specifically, we considered 6 test functions, rescaling the
test function so that the smallest intensity was $x$ and the largest
intensity was $y$, with $(x,y)$ set to either $(1/100, 3)$, $(1/8, 8)$
or $(1/128, 128)$.

For each combination of test function and intensity range, we
simulated 100 data sets. In the plots and tables below, we summarize
the error (MISE) in the estimates computed in the 100 data sets from
each simulation setting.

@@

Load the knitr, kableExtra, ggplot2 and cowplot packages.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
library(cowplot)
library(xtable)
```

@@

```{r spikes-table, results="asis"}
mise.s.table <- cbind(mise.s.1[methods],
                      mise.s.8[methods],
                      mise.s.128[methods])
rownames(mise.s.table) <- table.row.names
colnames(mise.s.table) <- table.col.names
kable(mise.s.table,format = "html",
  table.attr = paste("class=\"table\";","style=\"font-family: sans-serif;",
                     "width: auto; margin-left: auto; margin-right: auto\""))
```

@@

The combined violin-boxplots provide a more detailed summary of
the same results:

```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
m                  <- length(mise.ash.s.1)
method.labels      <- c("Haar-Fisz","BMSM","SMASH")
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
                                     mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
pdat128 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
create.violin.plots <- function (pdat1, pdat8, pdat128) {
  p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
		theme_cowplot() +
		theme(plot.title = element_text(size = 14,face = "plain"),
		      axis.line = element_blank())
  p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
		theme_cowplot() +
		theme(plot.title = element_text(size = 14,face = "plain"),
		      axis.line = element_blank())
  p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
        geom_violin(fill = "skyblue",color = "skyblue") +
        geom_boxplot(width = 0.15,outlier.shape = NA) +
        coord_flip() +
        labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
		theme_cowplot() +
		theme(plot.title = element_text(size = 14,face = "plain"),
		      axis.line = element_blank())
  return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))
}
create.violin.plots(pdat1,pdat8,pdat128)
```
